%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A general CV with all my experiences
%
% Based on the template of Leo Uieda's CV
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper]{article}

% Identifying information
\newcommand{\Title}{Curriculum Vit\ae}
\newcommand{\FirstName}{Ana Caroline}
\newcommand{\LastName}{Colombo}
\newcommand{\Initials}{AC}
\newcommand{\MyName}{\FirstName\ \LastName}
\newcommand{\Me}{\textbf{\LastName, \Initials}}  % For citations
\newcommand{\Email}{contact@acarolcolombo.com}
\newcommand{\Website}{acarolcolombo.com}
%\newcommand{\ORCID}{}
%\newcommand{\phone}{}
%\newcommand{\Affiliation}{}
%\newcommand{\Address}{}

% Names for citing coauthors
\newcommand{\Amanda}{De Oliveira, AR}
\newcommand{\Adriano}{Reimer, AE}
\newcommand{\Brandao}{Brandão, ML}
\newcommand{\Muthu}{Muthuraju, S}
\newcommand{\Rafael}{Almada, RC}
\newcommand{\Marcio}{Rodrigues, ML}
\newcommand{\Viviane}{Saito, VM}
\newcommand{\Teddy}{Talbot, T}
\newcommand{\Pag}{Rizzo, J}
\newcommand{\Zamith}{Zamith-Miranda, D}
\newcommand{\Va}{Silva, VKA}
\newcommand{\Jeremy}{Allegood, JC}
\newcommand{\Casadevall}{Casadevall, A}
\newcommand{\Maurizio}{Del Poeta, M}
\newcommand{\Josh}{Nosanchuk, JD}
\newcommand{\Kronstad}{Kronstad, JW}
\newcommand{\Nayara}{Barroca, NCB}
\newcommand{\Mariana}{Guarda, MD}
\newcommand{\Naiara}{Silva, NT}
\newcommand{\Antonella}{Rella, A}
\newcommand{\Tyler}{Normile, T}
\newcommand{\Luna}{Joffe, LS}
\newcommand{\Patricia}{Tavares, PM}
\newcommand{\Glauber}{Araújo, GRS}
\newcommand{\Susana}{Frases, S}
\newcommand{\Erika}{Orner, EP}
\newcommand{\Amir}{Farnoud, AM}
\newcommand{\Bettina}{Fries, BC}
\newcommand{\Brian}{Sheridan, B}
\newcommand{\Leo}{Nimrichter, L}
		
% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Disable hyphenation
\usepackage[none]{hyphenat}

% Control the font size
\usepackage{anyfontsize}

% Icon fonts (requires using xelatex or luatex)
\usepackage[fixed]{fontawesome5}
\usepackage{academicons}

% Template variables for styling
\newcommand{\TablePad}{\vspace{-0.4cm}}
\newcommand{\SoftwareTitle}[1]{{\bfseries #1}}
\newcommand{\TableTitle}[1]{{\fontsize{12pt}{0}\selectfont \itshape #1}}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\usepackage{environ}
\NewEnviron{EntriesTable}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.15\textwidth} p{0.85\textwidth}@{}}
    \BODY
\end{tabularx}
}

% Macros to add links
\newcommand{\DOI}[1]{doi:\href{https://doi.org/#1}{#1}}
\newcommand{\GitHub}[1]{\newline • Code: \faGithub\ \href{https://github.com/#1}{#1}}


% Macros to set the year and duration on the left column
\newcommand{\Duration}[2]{\fontsize{10pt}{0}\selectfont #1--#2}
\newcommand{\Year}[1]{\fontsize{10pt}{0}\selectfont #1}
\newcommand{\Ongoing}{}

% Define command to insert month name and year as date
\usepackage{datetime}
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Set the page margins
\usepackage[left=0.5in,right=0.5in,top=0.7in,bottom=0.7in]{geometry}

% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.1}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.2}

% Remove space between items in itemize and enumerate
\usepackage{enumitem}
\setlist{nosep}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Set fonts. Requires compilation with xelatex
%\usepackage{fontspec} % required to make older xelatex compile with UTF8

% Configure the font style for sections
\usepackage{sectsty}
\sectionfont{\vspace{0.1cm}\bfseries\fontsize{12pt}{0}\selectfont\uppercase}
\subsectionfont{\vspace{0.1cm}\mdseries\fontsize{12pt}{0}\selectfont\uppercase}

% Set the spacing for sections
%\usepackage{titlesec}
%\titlespacing{\section}{0pt}{0cm}{0.3cm}
%\titlespacing{\subsection}{0pt}{0.3cm}{0.3cm}

% Disable number of sections. Use this instead of "section*" so that the sections still
% appear as PDF bookmarks. Otherwise, would have to add the table of contents entries
% manually.
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Set fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\chead{
    \itshape
    \fontsize{10pt}{12pt}\selectfont
    \MyName
    \hspace{0.2cm} -- \hspace{0.2cm}
    \Title
    \hspace{0.2cm} -- \hspace{0.2cm}
    \monthyear\today
}
\rhead{}
\cfoot{\fontsize{10pt}{0}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

% Metadata for the PDF output and control of hyperlinks
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
    pdftitle={\MyName\ - \Title},
    pdfauthor={\MyName},
    linkcolor=blue,
    citecolor=blue,
    filecolor=black,
    urlcolor=MidnightBlue
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% No header for the first page
\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% HEADER
{\fontsize{20pt}{0}\selectfont \MyName}	\\[0.3cm]
\rule{\textwidth}{0.2pt}
\begin{minipage}[t]{0.595\textwidth}
	 email: \href{mailto:\Email}{\Email}
    \\
    website: \href{https://www.\Website}{\Website}
\end{minipage}
\begin{minipage}[t]{0.405\textwidth}
  \begin{flushright}
  Last updated: \monthyear\today
  \\
    %\Affiliation
	%\\
	%\Address
  \end{flushright}
\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Experience}

\begin{EntriesTable}
	
	\Duration{06/2019}{08/2019}  &
	\textbf{Arboretum Intern OR Education Department Intern}
	\newline
	\textit{Lyon Arboretum - Honolulu, HI, USA.}
	\newline
	Hybrid experience with part-time spent in the Education Department, and part-time spent across three other Departments: Grounds, Horticulture and Micropropagation and Seed Labs. \textbullet \ Developed a field-trip material for 3rd grade about plant adaptations \textbullet \ Learned about Hawaiian culture \textbullet \ Helped with k-12 summer camp \textbullet \ Guided tours through the arboretum \textbullet \ Participated in outreach at public events \textbullet \ Learned and Assisted with plant propagation techniques, identification of plants and maintenance of gardens and trails.
	\\
	
	\Duration{03/2019}{06/2019}  &
	\textbf{Provider Credentialing Assistant}
	\newline
	\textit{HMAA/HWMG - Honolulu, HI, USA.}
	\newline
	\textbullet \ Reached out to providers for credentialing in the health insurance company system \textbullet \ Organized data and files.
	\\
	
	\Duration{08/2016}{12/2017}  &
	\textbf{Research Support Specialist}
	\newline
	\textit{Stony Brook University, Stony Brook, NY, USA.}
	\newline   
	\textbullet \ Managed projects independently \textbullet \ Established external collaborations \textbullet \ Processed and analyzed data \textbullet \ Authored two published scientific papers \textbullet \ Presented in conferences \textbullet\ Conducted research in biomedical topics and performed laboratory experiments. 
	\\
	
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education}

\begin{EntriesTable}
    \Year{2018}  &
    \textbf{PhD in Biological Chemistry}, Federal University of Rio de Janeiro (UFRJ), Brazil.
    \\
    \Year{2014}  &
    \textbf{MSc in Psychobiology}, University of São Paulo (USP), Brazil.
    \\
    \Year{2011}  &
    \textbf{BSc in Biology}, State University of São Paulo (UNESP), Brazil.
    \\
    \Year{2010}  &
    \textbf{Licentiate degree in Biology}, State University of São Paulo (UNESP), Brazil.
    \newline
    \textit{Undergraduate level degree for teaching in primary and secondary education.}
    
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Research Experience}

\begin{EntriesTable}
	
	\Duration{2010}{2016}  &
	\textbf{Neuroscience, Behavior and Pharmacology}
	\newline
	 \textbullet \ Small animals models (mouse, rat and fish) \textbullet \ Behavioral tests (fear and anxiety, memory and depression), such as: catalepsy, open field and contextual fear conditioning, ultrasonic vocalization recording, elevated plus-maze and fear potentiated startle, novel object recognition, tail suspension \textbullet \ Local and systemic drug injection \textbullet \ Stereotaxic surgery \textbullet \ Perfusion \textbullet \ Histology and tissue staining.
	\\
	
	\Duration{2014}{2018}  &
	\textbf{Microbiology, Biochemistry and Immunology}
	\newline
	\textbullet \ Mouse model \textbullet \ Intranasal infection \textbullet \ Gavage technique \textbullet \ Systemic drug injection \textbullet \ Dissection \textbullet \ CFU \textbullet \ Histology and tissue staining \textbullet \ Galleria mellonela infection model \textbullet \ Primary culture of rat astrocytes and neurons \textbullet \ Cell line culture \textbullet \ Hybridoma culture \textbullet \ Immunocytochemistry and Immunohistochemistry \textbullet \ Dot blot \textbullet \ MTT assay \textbullet \ Antibody biotinylation \textbullet \ Cultivation of pathogen yeast \textbullet \ Media preparation \textbullet \ Urease and melanin assay \textbullet \ Fungi growth and pH tests \textbullet \ Polysaccharide isolation and quantification \textbullet \ Vesicle purification and quantification \textbullet \ Enzyme-linked immunosorbent assay (ELISA) and Dubois colorimetric assay  \textbullet \ Scanning Electron Microscopy (SEM)  \textbullet \ Thin-layer chromatography (TLC) \textbullet \ Western blot \textbullet \ Southern blot \textbullet \ Flow cytometry \textbullet \ Lipid extraction and quantification \textbullet \ DNA purification  \textbullet \ Biobalistic DNA delivery method 
	\\

	
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Awards}

\begin{EntriesTable}
	\Duration{2014}{2018}  &
	National Council for Scientific and Technological Development (CNPq), Brazil. \textbf{PhD Research Scholarship.}
	\\
	\Duration{2012}{2014}  &
	São Paulo Research Foundation (FAPESP), Brazil. \textbf{Masters Research Scholarship.}
	\\
	\Year{2012}  &
	National Council for Scientific and Technological Development (CNPq), Brazil. \textbf{Masters Research Scholarship.} (3 months)
	\\
	\Year{2010}  &
	Coordination for the Improvement of Higher Education Personnel (CAPES), Brazil. \textbf{Undergraduate Institutional Program of Teaching Initiation
		Scholarship.} (9 months)
	\\
	\Year{2009}  &
	State University of São Paulo (UNESP, Botucatu), Brazil. \textbf{Undergraduate Academic Support and Outreach Scholarship.} (6 months)
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Publications}

\begin{EntriesTable}
\Year{2019}  &
    \Me, \Antonella, \Tyler, \Luna, \Patricia, \Glauber, \Susana, \Erika, \Amir, \Bettina, \Brian, \Leo, \Marcio, \Maurizio.
 	\emph{Cryptococcus neoformans} glucuronoxylomannan and sterylglucoside are required for host protection in an animal vaccination model.
    \emph{mBio},
    \DOI{10.1128/mBio.02909-18}.
    \\
\Year{2019}  &
    \Nayara, \Mariana, \Naiara, \Me, \Adriano, \Brandao, \Amanda. Influence of aversive stimulation on haloperidol-induced catalepsy in rats.
    Accepted at \emph{Behavioural Pharmacology}.
   \DOI{10.1097/FBP.0000000000000462}.
    \\
\Year{2018}  &
    \Pag, \Me, \Zamith, \Va, \Jeremy, \Casadevall, \Maurizio, \Josh, \Kronstad, \Marcio.
    The putative flippase Apt1 is required for intracellular membrane
    architecture and biosynthesis of polysaccharide and lipids in
    \emph{Cryptococcus neoformans}.
    \emph{BBA - Molecular Cell Research},
    \DOI{10.1016/j.bbamcr.2017.12.007}.
    \\
\Year{2015}  &
	\Brandao, \Amanda, \Muthu, \Me, \Viviane, \Teddy.
	Dual role of dopamine D2-like receptors in the mediation of conditioned
	and unconditioned fear.
	\emph{FEBS Letters},
\DOI{10.1016/j.febslet.2015.02.036}.
	\\
	~ &
	\Me, \Marcio.
	Fungal colonization of the brain: anatomopathological
	aspects of neurological cryptococcosis.
	\emph{Annals of the Brazilian Academy of Sciences},
	\DOI{10.1590/0001-3765201520140704}.
	\\
\Year{2014}  &
	\Amanda, \Me, \Muthu, \Rafael, \Brandao.
	Dopamine D2-like receptors modulate unconditioned
	fear: Role of the inferior colliculus.
	\emph{Plos One},
	\DOI{10.1371/journal.pone.0104228}.
	\\
\Year{2013}  &
	\Me, \Amanda, \Adriano, \Brandao.
	Dopaminergic mechanisms underlying catalepsy, fear and anxiety: Do
	they interact?.
	\emph{Behavioural Brain Research},
	\DOI{10.1016/j.bbr.2013.10.002}.
	\\
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section*{Selected Publications}
%
%\subsection*{Peer-Reviewed}
%
%\begin{EntriesTable}
%	\Year{2019}  &
%	\Me, \Antonella, \textit{et al.}
%	\emph{Cryptococcus neoformans} glucuronoxylomannan and sterylglucoside are required for host protection in an animal vaccination model.
%	\emph{mBio},
%	 \DOI{10.1128/mBio.02909-18}.
%	\\
%	\Year{2015}  &
%	\Me, \Marcio.
%	Fungal colonization of the brain: anatomopathological
%	aspects of neurological cryptococcosis.
%	\emph{Annals of the Brazilian Academy of Sciences},
%	\DOI{10.1590/0001-3765201520140704}.
%	\\
%	\Year{2013}  &
%	\Me, \Amanda, \textit{et al.}
%	Dopaminergic mechanisms underlying catalepsy, fear and anxiety: Do
%	they interact?.
%	\emph{Behavioural Brain Research},
%	\DOI{10.1016/j.bbr.2013.10.002}.
%	\\
%\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{Teaching}
%
% \begin{EntriesTable}
%    \Duration{2018}{2019}  &
%    Botany -- Kindergarten to 4th Grade (Assistant Teacher)
%    \newline
%    Education Department at Lyon Arboretum, Honolulu, USA.
%   \\
%    \Year{2015}  &
%    Biochemistry -- Undergraduate in Medicine (Assistant Teacher)
%    \newline
%    Federal University of Rio de Janeiro, Brazil.
%    \\
%    \Year{2015}  &
%    Immune endocrine neuro system -- Graduate in Biochemistry (Group Coordinator)
%    \newline
%    Federal University of Rio de Janeiro, Brazil.
%    \\
%    \Year{2010}  &
%    Biology -- High School (Teacher and Assistant)
%    \newline
%    State School Professor Francisco Guedelha, Botucatu, Brazil.
%    \\
%    \Year{2007}  &
%    Literature -- Pre-university preparatory course (Teacher)
%    \newline
%    State University of São Paulo, Brazil.
%\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Teaching Internships}

\begin{EntriesTable}
	\Duration{10/2018}{03/2019}  &
	\textbf{Assistant Teacher} -- Kindergarten to 4th Grade
	\newline
	\textit{Education Department at Lyon Arboretum, Honolulu, USA.}
	\newline
	\textbullet \ Assisted and taught field trips and classes \textbullet \ Organized and managed the classrooms.
	\\
	\Year{2015 (10 classes)}  &
	\textbf{Assistant Teacher} -- Undergraduate Biochemistry
	\newline
	\textit{Federal University of Rio de Janeiro, Brazil.}
	\newline
	\textbullet \ Developed guided practice worksheets \textbullet \ Created and implemented formative assessment \textbullet \ Prepared and presented theoretical classes \textbullet \ Designed and applied final exams.
	\\
	\Year{2015 (10 classes)}  &
	\textbf{Group Supervisor} -- Graduate Immune-neuro-endocrine System 
	\newline
	\textit{Federal University of Rio de Janeiro, Brazil.}
	\newline
	\textbullet \ Guided and helped a group of seven students to prepare and teach theoretical and creative classes.
	\\
	\Duration{03/2010}{12/2010}  &
	\textbf{Assistant Teacher} -- Biology for High School students
	\newline
	\textit{State School Professor Francisco Guedelha, Botucatu, Brazil.}
	\newline
	\textbullet \ Helped to develop and organize the first science fair of the school \textbullet \ Taught theoretical and practical biology classes \textbullet \ Participated in group meetings \textbullet \ Helped to design and apply surveys to assess student's goals. 
	\\
	\Year{2007 (9 classes)}  &
	\textbf{Volunteer Teacher} -- Literature for a pre-university preparatory course 
	\newline
	\textit{State University of São Paulo, Brazil.}
	\newline
	\textbullet \ Prepared and taught classes.
	
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\subsection*{Workshops and Short Courses}

%\begin{EntriesTable}
%\Year{future}  &
%\Year{201}  &
%    Best Practices for Modern Open-Source Research Codes
%    \newline
%    AGU Fall Meeting 2018
%    \\
% 
%\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section*{Outreach and Volunteering}
%
%\begin{EntriesTable}
%\Duration{2018}{2019}  &
%    Volunteer for the Lyon Arboretum, Honolulu, USA -- \textbf{Gift Shop Clerk.}
%    \\
%\Duration{2018}{2019} &
%    Volunteer for the Lyon Arboretum, Honolulu, USA -- \textbf{Elementary School Field Trip Volunteer.}
%    \\
%\Year{2018}  &
%    Volunteer for the \textit{Goodwill Goes Glam} at Goodwill,
%    Honolulu, USA -- \textbf{Retail.}
%    \\
%\Year{2018} &
%    Volunteer for the \textit{Geographic Information System Day} at NOAA, Honolulu, USA -- \textbf{Assistant.} 
%	\\
%\Year{2017}  &
%	Volunteer for a special class about Brazil at Nassakeag Elementary School, Setauket, USA -- \textbf{Speaker/Teacher.}
%	\\
%\Year{2009}  &
%	Center of Regional Reference in Intestinal Inflammatory Disease at State University of São Paulo, Brazil -- \textbf{Patient survey.}
%	\\
%\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Volunteering and Outreach}

\begin{EntriesTable}
	\Duration{10/2018}{03/2019}  &
	\textbf{Assistant for Children's Education Program},
	%	\newline
	\textit{Lyon Arboretum, Honolulu, USA.}
	\newline
	\textbullet \ Taught hour long, elementary level classes \textbullet\ Assisted students with difficult tasks \textbullet \ Prepared classroom resources.
	\\
	\Duration{08/2018}{03/2019}  &
	\textbf{Gift Shop Clerk},
	%	\newline
	\textit{Lyon Arboretum, Honolulu, USA.}
	\newline
	\textbullet \ Greeted and helped visitors with general information \textbullet \ Operated the cash register \textbullet \ Organized the store. 
	\\
	\Year{2018}  &
	\textbf{Retail Helper for Goodwill Goes Glam event},
	%	\newline
	\textit{Goodwill, Honolulu, USA.}
	\newline
	\textbullet \ Duties included customer service and organizing sales inventory.
	\\
	\Year{2017}  &
	\textbf{Invited speaker},
	%	\newline
	\textit{Nassakeag Elementary School, Setauket, USA.}
	\newline
	\textbullet \ Created and presented a class about Brazil.
	\\
	\Year{2009}  &
	\textbf{Research Interviewer},
	%	\newline
	\textit{State University of São Paulo, Brazil.}
	\newline
	\textbullet \ Collected patient information \textbullet \ Explained research goals and consent form \textbullet \ Established contact between clinic and research group.
	\\
	\Duration{04/2007}{12/2010}  &
	\textbf{Accountant},
	%	\newline
	\textit{ Graduation Party Planning Committee, Brazil.}
	\newline
	\textbullet \ Surpassed the fundraising goal \textbullet \ Trusted for the position by peers \textbullet \ Helped to organize fundraising events  \textbullet \ Designed and sold products \textbullet \ Participated in regular meetings and
	committee's decisions.
	\newline
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Academic Service \& Affiliations}

\begin{EntriesTable}
\Year{2020} &
	Ad hoc referee of undergraduate scientific projects
	\newline
	Psychology
	\newline
	Federal University of São Carlos, Brazil.
	\\
\Year{2019} &
	Ad hoc referee of undergraduate scientific projects 
	\newline
	Psychology
	\newline
	Federal University of São Carlos, Brazil.
	\\
\Year{2018} &
    Ad hoc referee of undergraduate scientific projects 
	\newline
	Psychology
    \newline
    Federal University of São Carlos, Brazil.
    \\
\Year{2015} &
	Ad hoc referee of undergraduate scientific posters 
	\newline
	Microbiology
	\newline
	Federal University of Rio de Janeiro, Brazil.
	\\
\Year{2009} &
	Organizing committee of the XIII Biology Week
	\newline
	State University of São Paulo, Brazil.
	\\
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Continuing Education}

\begin{EntriesTable}
	\Year{2019 (1 month)}  &
	\textbf{101 Web Development} -- DevLeague - Honolulu, HI, USA.
	\\
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Additional Skills}

	\textbullet \ Bilingual (English and Portuguese) \textbullet \ Fundraising and Event Organization \textbullet \ Microsoft Office \textbullet \ Basic Python, JavaScript, HTML, CSS and \LaTeX\ \textbullet \ Basic Image Editing and Vector Graphics Software \textbullet \ Data Processing and Statistical Analysis


\end{document}